### 2016-10-19 methodsPaper/tex/materialsAndMethods.tex
Fixed a bug or two and wrapped text (for readability)

We report total change (averted or increased) in diability adjusted life years (DALYs) as an estimate of dissease burden change with alternative scenarions. To estimate DALYs we use a methodology adopted from previous US implementations of ITHIM  which scale Global Budern of Disease Estimates for the US to smaller populations using mortality rate ratios \cite{Maizlish2013}. Age, sex, and casuse specific mortalities were obtained form the CDC WONDER database for US metro counties for the years 2010-2014. Cells with less than 10 deaths were imputed using R's random integer generator.

>>>>

We report total change (averted or increased) in diability adjusted
life years (DALYs) as an estimate of dissease burden change with
alternative scenarions. To estimate DALYs we use a methodology adopted
from previous US implementations of ITHIM which scale Global Budern of
Disease Estimates for the US to smaller populations using mortality
rate ratios \cite{maizlish2013}. Age, sex, and casuse specific
mortalities were obtained form the CDC WONDER database for US metro
counties for the years 2010-2014. Cells with less than 10 deaths were
imputed using R's random integer generator.
